---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

An introduction of the data and a description of the trends/books/items you are choosing to analyze (and why!)

The data is recording different reading materials with different usage type like physical or digital. The trend I would like to analyze is the checkouts trend of digital, specifically Ebooks, to see in a modern days the portion of how many people choose to read electronic version materials.

### Summary Information

Write a summary paragraph of findings that includes the 5 values calculated from your summary information R script

These will likely be calculated using your DPLYR skills, answering questions such as:

- What is the average number of checkouts for each item?
- What is the month or year with the most/least checkouts for a book that you're interested in?
- What is the month or year with the most/least checkouts for ebooks?
- How has the number of print book checkouts changed over time?

Feel free to calculate and report values that you find relevant.

<<<<<<< HEAD
From the calculation I did, I find that "So You Want to Talk about Race (Unabridged)" is the digital book with the most monthly checkout amount(4903), and the book "Headphones / Seattle Public Library." is the physical book with the most monthly checkout amount(2115). Also, in 2017, the book with the most monthly checkout amount(988) is "In Building Device Checkout". Besides that, my favorite album 24K Magic has a highest checkout number at the year 2017. Last but not least, I find a increase trend of digital material checkout numbers over the checkout year, but in the year 2023, the number has a sudden decrease which might due to the data include checkouts only for the first two month of the year.
=======
From the calculation I did, I find that "So You Want to Talk about Race (Unabridged)" is the digital book with the most monthly checkout amount(4903), and the book "Headphones / Seattle Public Library." is the physical book with the most monthly checkout amount(2115). Also, in 2017, the book with the most monthly checkout amount(988) is "In Building Device Checkout". Besides that, my favorite album 24K Magic has a highest checkout number at the year 2017. Last but not least, I find a increase trend of Ebooks checkout number over the checkout year until the year 2020, but in the year 2023, the number has a sudden decrease which might due to the data include checkouts only for the first two month of the year.
>>>>>>> f2afe2726a70b07dfa780d25b9b2b7f9baba6532

### The Dataset

- Who collected/published the data?  
- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
- How was the data collected or generated?  
- Why was the data collected?  
- What, if any, ethical questions do you need to consider when working with this data?  
- What are possible limitations or problems with this data?   (at least 200 words)

The data was collected by Seattle Public Library, the parameters in this dataset include Usage Class, Checkout Type, Material Type, Checkout Year, Checkout Month, Checkouts, Title, ISBN, Creator, Subjects, Publisher, Publication Year. The digital checkout data is from various media vendors, the physical data is from The Legrady artwork data archives. The data was collected for checking the trends of checkouts of different book in different sources like physical and digital. The ethical question that might be facing is what the book's audiences is. When dealing with this, we need to be patient and reflecting the result using words that do not hurt their feelings.

The possible limitations with this data is there are many missing values that might be important when finding the trends that we needed. The missing value might form a false trend when we analyzing the data. Also the format of some variables are not the same, this cause a problem when we try to analyze the data that include the associated "untidy" data. We might need some time find a best way to clean up the data set before we start finding data visualization. Last but not least, we need to focus the category of the book, the physical and digital have different patterns and we need to be aware of what the observations belong to.

### First Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The first chart that you will create and include will show the trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

#### Observations:

```{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("chart1.R")}
```

This chart is aimed to check whether there is a increasing trend of the Ebooks checkout number in the dataset. The real condition seems to be a little bit different from what I thought, it is true that there is a increase from 2017 to 2020, but there is a slight decrease from 2020 to 2022, and a sudden decrease at 2023. This might due to the record is stopped at Feb 2023.

### Second Trends Over Time Chart

Include a chart. Make sure to describe why you included the chart, and what patterns emerged

The second chart that you will create and include will show another trend over time of your variable/topic/interest. Think carefully about what you want to communicate to your user (you may have to find relevant trends in the dataset first!). Here are some requirements to help guide your design:

- Show more than one, but fewer than ~10 trends
  - For example, two books, or 5 different mediums
- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear - legend title
In your .Rmd file, make sure to describe why you included the chart, and what patterns emerged

When we say "clear" or "human readable" titles and labels, that means that you should not just display the variable name.

Here's an example of how to run an R script inside an RMarkdown file:

#### Observations:

```{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("chart2.R")}
```

This chart is aimed to understand what kind of class people would like to checkout in the first month to see the trend of people choosing between physical or digital. The result would be suprising that people are more willing to choose physical version compared with digital version only exclude the year of 2021 and 2023.

### Your Choice

The last chart is up to you. It could be a line plot, scatter plot, histogram, bar plot, stacked bar plot, and more. Here are some requirements to help guide your design:

- You must have clear x and y axis labels
- The chart needs a clear title 
- You need a legend for your different line colors and a clear legend title

Here's an example of how to run an R script inside an RMarkdown file:

#### Observations: 

```{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("chart3.R")}
```

This chart is aimed to see which type of material is welcomed by the customers to checkout in the Jan od 2023, the result is books, Ebooks, and audiobooks. This is interesting since in the year of 2023 people still seems are more comfortable reading or listening to something that is a paper book or something that is closest to the form of book.
